---
title: "Lab: The 12 Days of Christmas"
output:
  prettydoc::html_pretty:
    theme: tactile
    highlight: github
    css: styles.css
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

# Packages for Functions
library(dplyr)
library(glue)
library(stringr)
library(purrr)
library(english)
library(prettydoc)
```


### A Test Dataset

Run the code below to load up a dataset called `xmas` that contains the crucial 
information about the gifts in the song. We will use this dataset to test out
our functions as we work on them.

```{r}
xmas <- read.csv("https://www.dropbox.com/s/e584pryn8evm1gz/xmas.csv?dl=1")
```

---
```{r}
xmas_small <- xmas %>% filter(Day < 3)
```

## Step One:  Plurals

Note that the gifts are listed in singular: for example, on day five the
narrator receives "five golden rings", but the entry in the dataset for the gift
on day 5 simply says "ring".  

Using the skeleton of the `pluralize_gift()` function, complete the code so that 
the function takes a gift and returns the appropriate plural. 

```{r}
# Function that takes a noun and makes it plural
# Arguments -- gift -- A string or vector of strings
# Return -- A string or vector of strings with the pluralized words

pluralize_gift <- function(gift){
if (str_detect(gift, "oo"))  {
gift <- gift %>%
  str_replace("oo", "ee")
} else if(str_detect(gift, "y$")){
  gift <- gift %>%
  str_replace("y$", "ies")
} else{
  gift <- glue::glue("{gift}s")
}
return(gift)
}


```





```{r}
purrr::map_chr(xmas$Gift.Item, pluralize_gift)
```


---


## Step Two: Creating sentences

Write a function called `make_phrase` that takes as input the necessary information, 
and returns a phrase.


```{r}
make_phrase <- function(num, num_word, item, verb, adjective, location) {
  
  ## Step 1: Replace NAs with blank strings
  verb <- str_replace_na(verb, "")
  location <- str_replace_na(location, "")
  adjective <- str_replace_na(adjective, "")
  
  ## Step 2: Pluralize the gift if needed
  ## Items with numbers larger than 1 should be pluralized
  ## Single items starting with a vowel should have "an" in front
  ## All other single items should have "a" in front
  
  vowel_start <- str_sub(item, 1, 1) %>% str_detect("[aeiou]")
  
  if (num > 1) {
    item <- pluralize_gift(item)
      num_word <- as.english(num)
  } else if (vowel_start) {
      num_word <- "an"
  } else {
    num_word <- "a"
  }
  return(glue::glue("{num_word} {adjective} {item} {verb} {location}") %>%
    str_squish())
}
```




```{r}
# add column to the existing dataset with the correct phrase for that day, using the make _phrase function we created
xmas <- xmas %>%
  #using the english package to turn the Day number into a word
  mutate(day.num = as.english(Day),
    Full.Phrase = pmap_chr(list(num = Day, num_word = as.english(Day), item = Gift.Item, verb = Verb, adjective = Adjective, location = Location), 
                           make_phrase)
  )
```


---


## Step Three:  Iteration.

Write a function called `sing_line` that takes as input:

* A dataset

* A number indicating which day to sing about

* The name of a column in the dataset that contains the phrases for each day.

```{r}
# Produces the string for one day of the song.
# Arguments -- dataset -- A data frame containing information about gifts
# Arguments -- line -- The number of the line for the day you want to sing about
# Arguments -- phrase_col -- The variable name for the column in the dataset that contains the gift phrases
# Return -- A string singing the line of the song with all gifts for the given day.

sing_line <- function(dataset, line, phrase_col){
  
  # Step 1: Setup the intro line
  
  num_word <- dataset$Day.in.Words
  
  intro <- glue::glue("On the {num_word} day of Christmas, my true love sent to me:")
  
  # Step 2: Sing the gift phrases
    phrases <- dataset %>% 
      pull({{phrase_col}})
    
    until_two <- paste0(glue::glue("{phrases[line:2]}"), collapse = "\n")
    
    last <- glue::glue("{phrases[1]}")
    
    one <- glue::glue("{phrases[1]}")
    
    full_phrase <- glue::glue("{intro[line]} \n{until_two} and \n{last}.")
      
    ## put it together
  if(line == 1){
    return(glue::glue("{intro[line]} \n{one}."))
  } else{
  return(full_phrase)    
  }
}

```

For example,


```{r}
sing_line(xmas, 
          line = 2, 
          phrase_col = Full.Phrase)

```

should return

```
On the second day of Christmas, my true love sent to me,
two turtle doves 
and a partridge in a pear tree.
```


## Step Four: Use Your Functions!

Run the following code to test out your functions! The output should be the 
lyrics for the entire 12 Days of Christmas song. 

```{r}
xmas2 <- xmas %>%
  mutate(
    day.num =  as.character(english::english(Day)), 
    Full.Phrase = pmap_chr(list(num = Day, 
                                num_word = day.num, 
                                item = Gift.Item, 
                                verb = Verb, 
                                adjective = Adjective, 
                                location = Location), 
                           make_phrase)
  )

map_chr(1:12, ~sing_line(xmas2, .x, Full.Phrase)) %>%
  str_c(collapse = "\n") %>%
  cat()

```


## Step Five: Show Me Your Work! 

#### Get it on GitHub

Github repository: https://github.com/zubaqar/twelvedays

